Busch, Khakhalin. Intrinsic temporal tuning

### 2019-06-03 reviews and responses.md

Previously a justification for the use of dynamic clamp was only given in the Discussion section; we now moved it to the end of Introduction.

@@

> Is the dynamic clamp current injection protocol mimicking the physiological synaptic
input? This should be stated.

We updated next sentence, stressing that the dynamic clamp protocol mimicked physiological synaptic inputs: "We used conductances of 4 different durations (100, 200, 500, and 1000 ms), and 3 different amplitudes (peak conductances of 0.2, 0.5, and 1.0 nS), matching the range of synaptic currents observed in tectal circuits in vivo (Xu et al. 2011; Khakhalin et al. 2014; Ciarleglio et al. 2015; see Methods)."

@@

> - I think the experiment in this study is pretty straightforward, but the description of the
results is not. As far as I can tell, tadpoles were exposed to different stimuli (flash,
looming, multisensory, etc.). Then, tectal neurons were stimulated using either 1)
dynamic clamp or 2) more physiologically through optic chiasm. This allowed the
investigators to assess firing when they changed the stimulus intensity and stimulus
duration of the dynamic clamp or the synaptic response to presynaptic stimulation.
They then looked how the different types of sensory experience influenced firing
responses. The rest is data analysis that looks at how the duration, amplitude, total
spiking, and synaptic input is changed in different sensory contexts and sensory
stimuli might interact. I think the text can be made much simpler so the basic design
is easier to grasp. I suggest thinking about what the take home point is for each
figure and craft the results section around those messages.

Thank you; we tried to follow this advice in this revised version of the manuscript!

> - There is also an inconsistent use terminology. For example, “spikiness” and
“excitability” are sometimes used in attempt to describe distinct cell characteristics,
but sometimes it seems like they are being used interchangeably. This makes
interpreting the written results difficult to follow.

As described in our responses to Reviewer 2, in this updated version, we consistently use "spikiness" as a name for the high-level variable, for the first time introduced in Figure 2C; we use "average number of spikes" for the average number of spikes; and "neuronal excitability" in all instances when we talk about the general, undelying idea of neuronal excitability. As the only exception to this rule, we opt for the word "spikiness" in the first paragraph of Introduction, to prime the reader for the use of this word later in the text.

@@

> - “Compared to control, neurons from animals exposed to visual stimuli had a flatter
amplitude tuning curve (Fig 1D,E).” What is the reader supposed to be looking at in
the figure? Is this referring to larger conductances for a fixed duration? I think this is
what the authors’ mean, but more intuitive descriptions that matches the figures or
vice versa is needed to make the whole results section easier to digest.

We improved the sentence:

"Compared to control, neurons from animals exposed to visual stimuli had a flatter amplitude tuning curve (less of a difference between columns of Figure 1D, or between curves in each individual panel of Figure 1E), as they did not increase their spiking as fast in response to larger conductances."

@@

> - Excessive wordiness makes the results difficult to read and interpret. For example,
on pg. 9, 4 paragraphs (411 words) are used to describe two graphs, each showing
a different linear relationship (Fig. 3E-F). Why not simply say, “A positive relationship
between temporal tuning and synaptic duration implies a co-tuning of preferr
parameters.”

Of these four paragraphs, the last one reports a negative result that is not shown in Figure 3. The first three paragraphs are indeed dedicated to panels Figure 3EF, but we cannot in a good faith replace them with one sentence, as the statement we make there is not statistically obvious. We believe that an attempt to gloss it over by pushing the statistical analysis to the methods section would not be fair. The issue, as we describe it, is that while graphs 3E and 3F have similar axes, and both show a linear dependency, they have opposite slopes. Had the slopes be the same, we would have just reported a correlation in one sentence. But with the data we have, we need to be more specific, as we observed that the within-group correlation is positive, yet the between-group correlation is negative: a situation that is not uncommon for large datasets, but that some readers may not be intimately familiar with.

We are aware that this section may read differently for different readers, and we received some conflicting advice in the past, about the level of details that is optimal for communicating this message. For example, readers who remember discussing Simpson's paradox in their statistics classes typically find our mentioning of this term helpful, while those who haven't encountered this term before, tend to find it distracting. For now, we opt to include it, even though it seems to be appreciated by only one half of our target audience. Nevertheless, in this new version of the paper, we shortened this section from 411 to 294 words.

@@

> - In reference to the text at the bottom of page10: Is it possible to include a summary
figure of data from the stepwise generalized linear model in Fig. 4? The purpose of
this part of the study was to try and identify electrophysiological mechanism(s) that
explain the tuning variables. The heart of Fig. 4 should be that they don’t, and figure
that captures this would be helpful.

We are not sure how this fact can be illustrated. We searched for papers that use stepwise linear models, and it seems that researchers do not typically include summary figures to describe combinatorial model optimization. Some papers that use this method include tables, listing R-squared, F, df, and p-values for every component, but as in our paper we are not particularly concerned with the precise composition of the model, we are not sure that a table like that would be useful. If you have some specific type of illustration in mind, please kindly describe it, or reference it. The only type of illustration we could come up with is a scatterplot that compares values predicted by the model to actual values, as shown on Figure 4E. Some technical papers sometimes also present the model information factor penalty as a function of the number of terms included in the model, but again, we are not sure how useful this type of presentation would be for our paper, as we are not particularly concerned with the composition of the model, and the quality of the information criterion minimum, as our main point here is that the prediction quality of this whole family of models is not great, and we cannot even overfit, as temporal tuning cannot be predicted from standard voltage-clamp-based electrophysiological variables.

For references, see for example: Stine, R. A. (2004). Model selection using information theory and the MDL principle. Sociological Methods & Research, 33(2), 230-260.

@@

> - If these data are interpreted as homeostatic (neurons became less excitable
following sensory experience), is there any evidence that tectal neurons have
different firing activities during the different kinds of sensory experience? For
example, does sound engage tectal neurons less than visual stimuli, and might this
explain some of the trends in the data?

This may indeed explain some of the trends in the data, but unfortately, as we described above, recording of tadpole tectal reponses to sounds does not seem to be possible in our lab, and is fundamentally technically problematic in principle. We can only guess that stimuli so different as flashes, looms, and sound clicks, would produce different responses in the tectum, as their dynamics is drastically different, and as they engage different circuits before reaching the tectum (retinal circuits for visual stimuli, hindbrain for acoustic), which undoubtedly shapes the dynamics of tectal activation (based on Khakhalin 2014, Felch 2016, Truszkowski 2017, Khakhalin 2019). We now make this point more clear by referencing it in the beginning of the paper (as described above), and then again, at the very end of Discussion, by describing how our observations can be used to predict actual, unobserved activation of the tectum during multisensory stimulation in vivo:

"Finally, based on the multisensory phenomena reported in this paper, we predict that even though multisensory stimulation tends to increase tectal responses in vitro (Felch et al., 2016; Truszkowski et al., 2017), it may reduce peak activation in vivo."
